---
title: "First own creations"
output: html_notebook
---

These are my first own creations without relying on previous commands or rather committing given orders.
Following is the introduction of some data, its organization and in the end its plot.

First action is to install necessary packages.

```{r}
library(tidyverse)
library(readxl)
```

Now let's read some downloaded data.

```{r}
Prices <- read_xlsx("/Users/JoostHaddinga_1/Desktop/University/SemesterII/Programming/R_Lectures/Rprogramming21_student/Lecture_3/sourcedata/Prices_Production_and_Labor.xlsx", skip=5)

```

Select the countries I want to use: United States, United Kingdom, Barbados, Afghanistan, China, Canada, Belgium, Austria, Belize

```{r}
Countries <-c("United States", "United Kingdom", "Barbados", "Afghanistan, Islamic Rep. of", "China", "Canada", "Belgium", "Austria", "Belize")

My_countries <- data.frame(Prices) %>%
  filter(Country %in% Countries) %>%
  select(Country, contains("Q"))


```

Now I have got the data I need to get with it.
First, let's rearrange the data.

```{r}
df1 <- pivot_longer(My_countries, !Country, names_to = "Quarter" , values_to = "CPI")

df1



```
```{r}
ggplot(df1, aes(x=Quarter, y= as.integer(CPI), colour=Country, group=Country))+geom_line()+theme_linedraw()+labs(title="My graph", caption="IMF database", y = "CPI")+scale_x_discrete(breaks=c('X2013Q1', 'X2014Q1', 'X2015Q1', 'X2016Q1', 'X2017Q1', 'X2018Q1', 'X2019Q1', 'X2020Q1'))


```


