---
title: "First own creations"
output: html_notebook
---

These are my first own creations without relying on previous commands or rather committing given orders.
Following is the introduction of some data, its organization and in the end its plot.

First action is to install necessary packages.

```{r}
library(tidyverse)
library(readxl)
```

Now let's read some downloaded data.

```{r}
Prices <- read_xlsx("/Users/JoostHaddinga_1/Desktop/University/SemesterII/Programming/R_Lectures/Rprogramming21_student/Lecture_3/sourcedata/Prices_Production_and_Labor.xlsx", skip=5)

```

Select the countries I want to use: United States, United Kingdom, Barbados, Afghanistan, China, Canada, Belgium, Austria, Belize

```{r}
Countries <-c("United States", "United Kingdom", "Barbados", "Afghanistan, Islamic Rep. of", "China", "Canada", "Belgium", "Austria", "Belize")

My_countries <- data.frame(Prices) %>%
  filter(Country %in% Countries) %>%
  select(Country, contains("Q"))


```

Now I have got the data I need to get with it.
First, let's rearrange the data.

```{r}
df1 <- pivot_longer(My_countries, !Country, names_to = "Quarter" , values_to = "CPI")

df1



```
```{r}
ggplot(df1, aes(x=Quarter, y= as.integer(CPI), colour=Country, group=Country))+geom_line()+theme_linedraw()+labs(title="My graph", caption="IMF database", y = "CPI")+scale_x_discrete(breaks=c('X2013Q1', 'X2014Q1', 'X2015Q1', 'X2016Q1', 'X2017Q1', 'X2018Q1', 'X2019Q1', 'X2020Q1'))


```

First graph worked ok. Nothing special but a satisfying start. Maybe I can do some more.
I need different data.

```{r}
data_x <- read_xlsx("/Users/JoostHaddinga_1/Desktop/University/SemesterII/Programming/R_Lectures/Rprogramming21_student/Lecture_3/sourcedata/Interest_Rates.xlsx", skip=5) %>%
  select(Country, "2014", "2015","2017", "2018", "2020") %>%
  slice(54:63)

data_x
```
```{r}
data_xy <- data.frame(data_x) %>%
  mutate('New Zealand' = as.factor(ifelse(Country == "New Zealand", 1, 0))) %>%
  rename("2014" ="X2014", "2015" = "X2015", "2017" = "X2017", "2018" = "X2018", "2020"="X2020")
  


data_xy
```

```{r}
data_z <- data.frame(pivot_longer(data_xy, '2014':'2020', names_to = "Year", values_to = "Interest Rate"))

data_z
```
Make a plot
```{r}
ggplot(data_z, aes(x=as.integer(Year), y= as.integer(Interest.Rate), color=Country, alpha=New.Zealand))+geom_line()+theme_bw()+labs(x="Year", y="Interest rate p. a.", title="Interest rates over time", subtitle = "Analysis by Joost Haddinga", caption = "source: IMF database")+scale_alpha_manual(values=c("1" = 2.5, "0"=0.4))+scale_colour_manual(values=c("New Zealand"="black", "Norway" ="green", "Nepal"="lightblue", "Mexico"="red", "Papua Neuguinea"="orange", "Niger"="318954", "Nigeria"="721092", "Mongolia"="567890", "Moldova, Rep. of"="874321", "Mauritius" ="043479"))
```

Now I can also combine both datasets

```{r}
CPI_2020 <- select(Prices, Country,"2020")
Interest_2020 <- read_xlsx("/Users/JoostHaddinga_1/Desktop/University/SemesterII/Programming/R_Lectures/Rprogramming21_student/Lecture_3/sourcedata/Interest_Rates.xlsx", skip=5) %>%
  select(Country, "2020")

```
Put data sets together
```{r}
Combined <- merge(CPI_2020, Interest_2020, by="Country") %>%
  rename("CPI"="2020.x", "Intpa"="2020.y")
 

Combined
```
Choose countries of interest
```{r}
Interest <- c("Canada", "Chile", "Colombia", "Georgia", "Honduras", "Indonesia", "Israel", "Nepal", "Rwanda", "Turkey")

Combined_1 <- filter(Combined, Country %in% Interest)

Combined_1
```

Make a last plot
```{r}
ggplot(Combined_1, aes(x=as.integer(CPI), y=as.integer(Intpa), colour=Country))+geom_point()+theme_get()+labs(x="Price level", y="Interest rate p. a.", title = "The world in 2020",caption="Own creation",subtitle= "Exploring possible correlations between price level and interest rates")
```

